Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-07-01 answer-to-reviewers.tex

This is expected as the general task considered by the authors is probably NP-hard (e.g. it should be possible to map it somehow to an inference in a credal network, see for instance Maua' et al., JAIR 2014). Yet, I miss a deeper discussion about the values of the parameters of the problem for which a brute-force computation of $\tilde{n}$ in Eq. 10 can be avoided. The authors say that this is the case in the 'vast majority' of the time points, but this is a strong claim, which deserves a discussion.

Of course, the discussion in S6.2 and the examples in S7 are doing something in this direction, but this is not enough.

A theoretical or empirical analysis should be necessarily added to convince the reader about the practical applicability of the result.
An idea might be a non-brute-force, approximate, approach (e.g., some sampling-based inner approximation). In the discrete case, such sampling can be drastically improved by sampling only on the extreme distribution (of the convex credal sets). This is less straightforward with continuous parameter, but it should be possible to do something even in this case (and I guess some paper by Alessio Benavoli can give direction about that).

\medskip
\emph{***We have added some first considerations on the question of how often we have to resort to numerical optimization in Appendix~C,
and now also give computation times for our examples in Section~7.2.}\\

\emph{***On the last note, by considering only the parametric Beta distributions,
we are already working with the extreme points of the credal sets induced by $\PktZ$.}
%in this continuous setting, the extreme points of the prior parameter set
%are the four Beta priors corresponding to combinations of $\yzl_{k,t_j}$ and $\yzu_{k,t_j}$ with $\nzl_{k,t_j}$ and $\nzu_{k,t_j}$,
%but the posterior parameter set is not convex
%
%most work by Alessio Benavoli concerns near-noninformative sets of priors, while we deal with ***
\medskip

@@

- The expression ''in an arbitrarily fine grid of time points'' in the introduction might sound a bit obscure

\medskip
\emph{We wanted to express here that there are no restrictions on time grid density,
and do not see the need to phrase this otherwise.}
\medskip

- \verb+\overline{x}+ for arrays might be a bit confusive in a IP paper, why not to use \verb+\vec{}+ or \verb+\bm{}+?

\medskip
\emph{Agreed, we changed the notation in Section~2 to use $\vec{x}$ in place of $\underline{x}$ for state vectors.}
\medskip

@@

- $n^{(n)}$ is weird (page 7)

\medskip
\emph{Agreed, but we wish to be consistent with previous literature on sets of conjugate priors and so prefer to keep this notation.}
\medskip

- Sec 4, why not to cite that the re-parametrization is based on the re-parametrization a' la Walley for the Dir distribution?

\medskip
\emph{Agreed. This parametrization for conjugate priors in exponential families has been known for a long time
(see, e.g., Diaconis \& Ylvisaker 1979),
but Walley (1991, \S 5.3) showed its usefulness for the imprecise Beta model, and then for the IDM.
}
\medskip

@@

- I would shape the example at the end of S4 in an example environment

\medskip
\emph{As we have our main examples in Section~7 in a separate subsection,
putting the example at the end of Section~4 would be awkward as
it would remain be the sole example in an example environment.}
\medskip

@@

- I see the issues related to the improper priors in the vacuous case, yet in the discussion of this issue I miss a link with Walley's IDM (or IBM \ldots).

\medskip
\emph{Agreed, we now refer to the literature on near-noninformative sets of priors (second-to-last paragraph of Section~5).}
\medskip

@@

- Why bold R for the R software?

\medskip
\emph{Agreed, we now use} \verb+\textsf{R}+ \emph{which seems to be the standard.}
\medskip

@@

* My main (and only substantial) comment about the paper is that it starts by seeling advantages of the survival signature, which are then completely forgotten since all mathematical developments concern independent components. Also, it seems to me that some points are a bit "oversold", for instance while I agree that the dependence of identical component types or between component types can easily be integrated, some other kind of dependence are impossible to implement (for instance, dependencies related to the position of components within the system, which are quite likely to occur in practice). I would therefore like the authors to 1) perhaps also explain the limitations of the survival signature and 2) add some (small?) discussion about what becomes of the current problem when independence between all components do not hold anymore. More specifically:

\medskip
\emph{We think that here the reviewer does not fully acknowledge the central benefit of the survival signature,
which is present also for independent components:
%Information on the system layout (which does not change over time) is fully separated from (time-dependent) component failure probabilities.}
It allows straightforward and efficient computation of the system survival by separating the (time-invariant) system structure from the time-dependent failure probabilities of components.}
\medskip

- top of P5: it would be fair to mention that dependencies related to component positions cannot easily be integrated to the signature (or at least I do not see how, if this is doable a reference/explanation should be provided.

\medskip
\emph{We added a paragraph at the end of Section~2 to address this point.}
\medskip

@@

- P6, 38/40: from here independence is assumed in the rest of the paper. It would be fair to discuss what extensions to non-independent cases are easy/difficult to produce, otherwise the advantage previously put forward of survival signatures simply disappears when adopting the author proposal.

\medskip
\emph{The crucial advantage of the survival signature approach is used throughout the paper, namely that it ensures all aspects of the system design are taken into account. It is indeed assumed, from the location indicated on, that components of the same type have conditionally independent and identically distributed failure times, conditional on the parameters $p_t^k$. This is a pretty standard assumption in reliability theory and we feel it is appropriate in this paper. However, crucially the approach presented enables learning about the parameters $p_t^k$ and keeps a dependence between the failure times of the components of the same type in the system, as common in Bayesian predictive distributions for multiple future observations.}
\medskip

* Perhaps mention somewhere (P19 or somewhere after?) that the elicited prior somehow correspond to a p-box? During my reading, I was actually reading to which extent results concerning p-boxes in general could not be useful in this setting.

\medskip
\emph{The sequence of $\yzl_{k,t_j}$ and $\yzu_{k,t_j}$ may seem indeed similar to a p-box.
However, we do not model prior knowledge about the reliability function of component type $k$
as the set of reliability functions bounded by $\yzl_{k,t_j}$ and $\yzu_{k,t_j}$.
Instead, we assume a set of Beta priors at each time point $t_j$ with means bounded by $\yzl_{k,t_j}$ and $\yzu_{k,t_j}$
and prior strengths bounded by $\nzl_{k,t_j}$ and $\nzu_{k,t_j}$.
This set of Beta priors for each $t_j$ can well be seen as a parametric p-box.
The parametric choice has the advantage that observed component lifetime data can be taken into account via the Generalized Bayes Rule update,
and that posterior predictive probabilities $P(C^k_t = l_k \mid \yktz, \nktz, s^k_t)$ needed for computation of system survival
are easily obtained as Beta-Binomial probabilities.
One could indeed use any p-box in place of our set of Beta priors for each $t_j$,
but we doubt that it would be nearly as tractable as our approach.}
\medskip

@@

* P19, L56: where $\to$ when

\medskip
\emph{Fixed, thanks.}
\medskip

* Figures 5,6,7: since T1,T2 always follow the same behaviour, perhaps put them only once?

\medskip
\emph{We decided to leave the figures as they are, to allow them to be interpreted on their own,
without the need to switch between different figures.
Specifically, each complete figure allows to relate any jump in the system reliability function bounds
to the corresponding jump in either of the component reliability function bounds.}
\medskip

### 2016-07-01 ijar-npb-ms.tex
all reviewers' remarks addressed except the computational complexity remark

The parametrisation of the Beta distribution used above is common,
and allows $\alpha^k_t$ and $\beta^k_t$ to be interpreted as
hypothetical numbers of functioning and failed components of type $k$ at time $t$, respectively.
However, when we generalise to sets of priors in the sequel,
it is useful to consider a different parametrisation.

@@

Furthermore, with sets of Beta priors it is also possible
to express prior ignorance
by letting $\yktzl \to 0$ and $\yktzu \to 1$
for some or all $t \in {\cal T}$.
(Note that it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$,
as this can lead to improper posterior predictive distributions.
For example, at any $t < \min(\vec{t}^k)$,
we would have $\yktnu = 1$, leading to one argument of the Beta function
in the denominator of \eqref{eq:postpredCny} being zero.)
These limits for $\yktz$ imply we are only prepared to give trivial bounds for the functioning probability
and do not wish to commit to any specific knowledge about $p^k_t$ \emph{a priori}.
This provides a more natural choice of `noninformative' prior over $[0,1]$ than the usual choice of
a Beta prior with $\alpha^k_t = \beta^k_t = 1$ (or $\nktz = 2$, $\yktz = 0.5$).
Such a prior for all $t \in {\cal T}$ actually reflects a belief that the component reliability function
is on average 1/2 for all $t$, which is not an expression of ignorance, but rather a very specific (and arguably peculiar) prior belief.

@@

\section{Practical Usage and Examples}
\label{sec:examples}
%***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},

@@

The methods of this paper have been implemented in the \textbf{R}
\citep{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT},
providing an easy to use interface for reliability practitioners.  The
primary function, which computes the upper and lower posterior
predictive system survival probabilities as in \eqref{eq:LwrSysPost}, is
named \texttt{nonParBayesSystemInferencePriorSets()}.  The user
specifies the times at which to evaluate the bounds, the survival
signature ($\Phi(\cdot)$), the component test data ($\vec{t}^1, \ldots,
\vec{t}^K$), and the prior parameter set for each component type and
time ($\PtZi{k}$, via $\nzu_{k,t}, \nzl_{k,t}, \yzu_{k,t}$, and
$\yzl_{k,t}$).  All computations of $\lRsys$
and $\uRsys$ at different time points are performed in parallel
automatically when the CPU has multiple cores and making automatic
use of the theoretical results in Section \ref{sec:setsofrel} where
applicable, performing exhaustive search in the few cases they are not.

@@

Gero Walter was supported by the DINALOG project
``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'' (CAMPI).

@@

Functions which make it easy to use the methods of this paper
have been added to the \textbf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}.
There are two functions of particular note: \texttt{computeSystemSurvivalSignature}
and, implementing the result from Appendix~\ref{ap:proofs} above, \texttt{nonParBayesSystemInferencePriorSets}.

>>>>

The parametrisation of the Beta distribution used above is common,
and allows $\alpha^k_t$ and $\beta^k_t$ to be interpreted as
hypothetical numbers of functioning and failed components of type $k$ at time $t$, respectively.
However, as recognized by \citep[\S 5.3]{1991:walley}, when we generalise to sets of priors in the sequel,
it is useful to consider a different parametrisation.

@@

Furthermore, with sets of Beta priors it is also possible
to express prior ignorance
by letting $\yktzl \to 0$ and $\yktzu \to 1$
for some or all $t \in {\cal T}$.
Such models are called \emph{near-noninformative} or \emph{near-ignorance models} in the imprecise probability literature
(see \citet[\S5.3.2]{1991:walley} for Beta priors,
and \citet{2012:benavolizaffalon,2015:benavolizaffalon} for exponential family priors),
as they provide vacuous bounds only for a certain class of inferences,
and the choice for the prior strength parameter $\nktz$ influences posterior inferences.
(Note that it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$,
as this can lead to improper posterior predictive distributions.
For example, at any $t < \min(\vec{t}^k)$,
we would have $\yktnu = 1$, leading to one argument of the Beta function
in the denominator of \eqref{eq:postpredCny} being zero.)
The limits $\yktzl \to 0$ and $\yktzu \to 1$ imply we are only prepared to give trivial bounds for the functioning probability
and do not wish to commit to any specific knowledge about $p^k_t$ \emph{a priori}.
This provides a more natural choice of `noninformative' prior over $[0,1]$ than the usual choice of
a Beta prior with $\alpha^k_t = \beta^k_t = 1$ (or $\nktz = 2$, $\yktz = 0.5$).
Such a prior for all $t \in {\cal T}$ actually reflects a belief that the component reliability function
is on average 1/2 for all $t$, which is not an expression of ignorance, but rather a very specific (and arguably peculiar) prior belief.

@@

\section{Practical Usage and Examples}
\label{sec:examples}

@@

The methods of this paper have been implemented in the \textsf{R}
\citep{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT},
providing an easy to use interface for reliability practitioners.  The
primary function, which computes the upper and lower posterior
predictive system survival probabilities as in \eqref{eq:LwrSysPost}, is
named \texttt{nonParBayesSystemInferencePriorSets()}.  The user
specifies the times at which to evaluate the bounds, the survival
signature ($\Phi(\cdot)$), the component test data ($\vec{t}^1, \ldots,
\vec{t}^K$), and the prior parameter set for each component type and
time ($\PtZi{k}$, via $\nzu_{k,t}, \nzl_{k,t}, \yzu_{k,t}$, and
$\yzl_{k,t}$).  All computations of $\lRsys$
and $\uRsys$ at different time points are performed in parallel
automatically when the CPU has multiple cores and making automatic
use of the theoretical results in Section \ref{sec:setsofrel} where
applicable, performing exhaustive search in the few cases they are not.

@@

Gero Walter was supported by the DINALOG project CAMPI
(``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'').

@@

Functions which make it easy to use the methods of this paper
have been added to the \textsf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}.
There are two functions of particular note: \texttt{computeSystemSurvivalSignature}
and, implementing the result from Appendix~\ref{ap:proofs} above, \texttt{nonParBayesSystemInferencePriorSets}.
